On the properties of projectile motion and quadratic air resistance

### 2016-02-21 Paper/main.tex
pi

	For the SAT approximation we can notice the same errors as in the HAT approximation but worth noting is that the errors somewhat cancel out. This is due to us overestimating the horizontal air resistance at $\theta \approx 0$ because $\sqrt{2}u > \sqrt{u^2}$ and underestimating the vertical air resistance at $|\theta| < \frac{pi}{4}$ because $\sqrt{2}|w|w < \sqrt{u^2}$. Both of these error are products of the approximation $u \approx w$ at all times. This could be partially solved by a unit step function as detailed in section \ref{seq:plotHAT}. The difference in range is $0.19\,m = 3.8\,\%$.

>>>>

	For the SAT approximation we can notice the same errors as in the HAT approximation but worth noting is that the errors somewhat cancel out. This is due to us overestimating the horizontal air resistance at $\theta \approx 0$ because $\sqrt{2}u > \sqrt{u^2}$ and underestimating the vertical air resistance at $|\theta| < \frac{\pi}{4}$ because $\sqrt{2}|w|w < \sqrt{u^2}$. Both of these error are products of the approximation $u \approx w$ at all times. This could be partially solved by a unit step function as detailed in section \ref{seq:plotHAT}. The difference in range is $0.19\,m = 3.8\,\%$.
